Methods to prioritise pop-up active transport infrastructure

### 2020-06-19 article.Rmd
Fix table

```{r commonplace, fig.cap="Screenshot from the website salfordliveablestreets.commonplace.is to support local responses to the COVID-19 pandemic, including the prioritisation of pop-up active transport infrastructure."}
# knitr::include_graphics("https://user-images.githubusercontent.com/1825120/81451234-ed82d200-917b-11ea-977d-fff1665378c5.png")
# download.file("https://user-images.githubusercontent.com/1825120/81451234-ed82d200-917b-11ea-977d-fff1665378c5.png", "saferstreets.png")
knitr::include_graphics(c(
  "figures/saferstreets.png",
  "figures/widenmypath-bristol.png"
  ))
```

@@

```{r t1, results='asis'}
# rj %>%
#   st_drop_geometry() %>%
#   # select(name, highway_type, maxspeed, cycling_potential, width) %>%
#   table1::table1(~ highway_type + cycling_potential + width + n_lanes | maxspeed, data = ., )
# ut = "https://user-images.githubusercontent.com/1825120/81476961-c32d2500-920c-11ea-8430-94c3afc2e27d.png"
# knitr::include_graphics(ut)
# system(paste("wget ", ut))
knitr::include_graphics("81476961-c32d2500-920c-11ea-8430-94c3afc2e27d.png")
```

@@

```{r gsub, fig.height=3, fig.cap="Illustration of geographic subsetting based on administrative boundaries (left), distance to a central point (middle) and distance to city centre or key destinations (right). Radii of 5 km, 8 km and 10 km are shown for reference (note that some roads within 10 km of the center are outside the regional boundary)."}
# nrow(r_central)
# nrow(rj)
square = stplanr::geo_bb(shp = city_centre_buffer)
r_main_region_key = r_main_region[city_key_buffer, ]
r_main_city = r_main_region[region, ]
m1 = tm_shape(r_main_city) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_shape(region) + tm_borders(col = "black", lwd = 2) +
  tm_shape(square) + tm_borders(lty = 3) +
  tm_scale_bar() 
# m1
m2 = tm_shape(r_main) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_shape(city_centre_buffer_small) + tm_borders(lty = 2) +
  tm_shape(city_centre_buffer_large) + tm_borders(lty = 2) +
  tm_shape(region) + tm_borders(col = "black", lwd = 2) +
  tm_shape(city_centre_buffer) + tm_borders() +
  tm_scale_bar() +
  tm_layout(legend.show = FALSE)
m3 = tm_shape(r_main_region_key) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_shape(city_centre_buffer) + tm_borders(lty = 2) +
  tm_shape(city_centre_buffer_small) + tm_borders(lty = 2) +
  tm_shape(city_centre_buffer_large) + tm_borders(lty = 2) +
  tm_shape(city_key_buffer) + tm_borders() +
  tm_shape(region) + tm_borders(col = "black", lwd = 2) +
  tm_shape(h_leeds) + tm_dots(size = 0.5) +
  tm_scale_bar() +
  tm_layout(legend.show = FALSE)
# this take aaaages to render...
tmap_arrange(m1, m2, m3, nrow = 1)
```

@@

An illustration of the scale of the results is shown in Figure \@ref(fig:facets), which shows the results for six major cities in England.
Local authorities are planning new pop-up cycleways informed by a range of sources of evidence, including the Rapid Cycleway Prioritisation Tool, and in many cases the plans match the routes highlighted by our tool.^[
[Kirkstall Road](https://www.bbc.co.uk/news/uk-england-leeds-52577554) in Leeds and [Jamaica Road](https://www.se16.com/6208-work-starts-on-54m-cycleway-along-jamaica-road) in London are a couple of examples.
Many more examples can be found on posts mentioning the tool on [social media](https://twitter.com/search?q=cyipt.bike%2Frapid).
]

>>>>

```{r commonplace, fig.cap="Screenshots from the websites widenmypath.com (top) and salfordliveablestreets.commonplace.is (bottom) to support local responses to the COVID-19 pandemic, including the prioritisation of pop-up active transport infrastructure.", fig.show='hold'}
# knitr::include_graphics("https://user-images.githubusercontent.com/1825120/81451234-ed82d200-917b-11ea-977d-fff1665378c5.png")
# download.file("https://user-images.githubusercontent.com/1825120/81451234-ed82d200-917b-11ea-977d-fff1665378c5.png", "saferstreets.png")
knitr::include_graphics(c(
  "figures/widenmypath-bristol.png",
  "figures/saferstreets.png"
  ))
```

@@

```{r t1, results='asis'}
# rj_leeds = readRDS("r_main_leeds.Rds")
# rj_leeds %>%
#   st_drop_geometry() %>% 
#   mutate(`width (m)` = width) %>% 
#   # select(name, highway_type, maxspeed, cycling_potential, width) %>% 
#   table1::table1(~ highway_type + cycling_potential + `width (m)` + n_lanes | maxspeed, data = ., )
# ut = "https://user-images.githubusercontent.com/1825120/81476961-c32d2500-920c-11ea-8430-94c3afc2e27d.png"
# knitr::include_graphics(ut)
# system(paste("wget ", ut))
knitr::include_graphics("figures/table1.png")
```

@@

```{r gsub, fig.height=3, fig.cap="Illustration of geographic subsetting based on administrative boundaries (left), distance to a central point (middle) and distance to city centre or key destinations (right). Radii of 5 km, 8 km and 10 km are shown for reference (note that some roads within 10 km of the center are outside the regional boundary)."}
# nrow(r_central)
# nrow(rj)
square = stplanr::geo_bb(shp = city_centre_buffer)
r_main_region_key = r_main_region[city_key_buffer, ]
r_main_city = r_main_region[region, ]
m0 = tm_shape(r_main_city) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_layout(legend.only = TRUE)
m1 = tm_shape(r_main_city) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_shape(region) + tm_borders(col = "black", lwd = 2) +
  tm_shape(square) + tm_borders(lty = 3) +
  tm_scale_bar() +
  tm_layout(legend.show = FALSE)
# m1
m2 = tm_shape(r_main) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_shape(city_centre_buffer_small) + tm_borders(lty = 2) +
  tm_shape(city_centre_buffer_large) + tm_borders(lty = 2) +
  tm_shape(region) + tm_borders(col = "black", lwd = 2) +
  tm_shape(city_centre_buffer) + tm_borders() +
  tm_scale_bar() +
  tm_layout(legend.show = FALSE)
m3 = tm_shape(r_main_region_key) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_shape(city_centre_buffer) + tm_borders(lty = 2) +
  tm_shape(city_centre_buffer_small) + tm_borders(lty = 2) +
  tm_shape(city_centre_buffer_large) + tm_borders(lty = 2) +
  tm_shape(city_key_buffer) + tm_borders() +
  tm_shape(region) + tm_borders(col = "black", lwd = 2) +
  tm_shape(h_leeds) + tm_dots(size = 0.5) +
  tm_scale_bar() +
  tm_layout(legend.show = FALSE)
# this take aaaages to render...
tmap_arrange(m0, m1, m2, m3, nrow = 1, widths = c(0.1, 0.3, 0.3, 0.3))
```

@@

After initially developing the method for a single city, we applied the methods nationwide.
An illustration of the scale of the results is shown in Figure \@ref(fig:facet), which shows the results for six major cities in England, including existing cycleway and 'cohesive network' layers, described on the tool's website [cyipt.bike/rapid](https://www.cyipt.bike/rapid/).
Local authorities are planning new pop-up cycleways informed by a range of sources of evidence, including the Rapid Cycleway Prioritisation Tool, and in many cases the plans match the routes highlighted by our tool.^[
[Kirkstall Road](https://www.bbc.co.uk/news/uk-england-leeds-52577554) in Leeds and [Jamaica Road](https://www.se16.com/6208-work-starts-on-54m-cycleway-along-jamaica-road) in London are a couple of examples.
Many more examples can be found on posts mentioning the tool on [social media](https://twitter.com/search?q=cyipt.bike%2Frapid).
]

```{r facet, fig.cap="Maps showing existing, disjointed cycleway networks (green), potential cycleway routes on wide roads according to the Rapid Cycleway Prioritisation Tool (blue) and cohesive networks (purple) in 6 major cities"}
knitr::include_graphics("figures/facet-output.png")
```
